Formalizing Stack Safety as a Security Property

### 2023-02-03 submission5/core.tex
First diagram, and macros for it

For a newly active function, every element that is available for use but uninitialized
is seen as \(\unsealed\). From the perspective of the caller, the callee has no obligations
regarding its use of \(\unsealed\) elements, but the callee itself \apt{???}

@@

@@

      \}}
  \end{subfigure}
  \begin{subfigure}{\columnwidth}
    \begin{tabular}{r l | l}
      \labeledrow{0:}{addi sp,sp,-20}{\(\mathbf{alloc} ~ (-20,20)\)}
      \labeledrow{4:}{sd ra,12(sp)}{}
      \labeledrow{8:}{sw a0,8(sp)}{}
      \labeledrow{12:}{sw zero,4(sp)}{}
      \labeledrow{16:}{jal f,ra}{\(\mathbf{call} ~ \emplist \)}
      \labeledrow{20:}{sw a0,0(sp)}{}
      \labeledrow{24:}{lw a4,4(sp)}{}
      \labeledrow{28:}{li a5,42}{}
      \labeledrow{32:}{bne a4,a5,L1}{}
      \labeledrow{36:}{lw a0,8(sp)}{}
      \labeledrow{40:}{sw a0,out}{}
      \labeledrow{44:}{j L2:}{}
      \labeledrow{L1, 48:}{lw a0,0(sp)}{}
      \labeledrow{52:}{sw a0,out}{}
      \labeledrow{L2, 56:}{ld ra,12(sp)}{}
      \labeledrow{60:}{addi sp,sp,20}{\(\mathbf{dealloc} ~ (0,20)\)}
      \labeledrow{64:}{jalr ra}{\(\mathbf{return}\)}
    \end{tabular}
  \end{subfigure}
  \begin{subfigure}{\columnwidth}
    \includegraphics[width=\columnwidth]{stacklayout.png}
  \end{subfigure}

\caption{Example: C and assembly code for {\tt main}, and layout of its stack frame; addresses increase to the right and the stadk grows to the left.\apt{Needs machine-set diagram.}}
\label{fig:main}
\end{figure}

%Figure \ref{fig:RISCVregs} gives an example division of the RISC-V registers into
%security classes.  APT: Don't think we need this figure.

@@

  \caption{Example: assembly code alternatives for {\tt f} as an attacker.
  }
  \label{fig:f}
\end{figure}

@@

The initial view \(V_0\) maps all stack addresses below \(\SP\) to \(\unsealed\) and the remainder of
memory to \(\public\). The sole used argument register, {\tt a0}, is mapped to \(\object\);
other caller-save registers are mapped to \(\unsealed\) and callee-save registers to \(\sealed\).
Step 1 allocates a word each for {\tt secret}, {\tt sensitive}, and {\tt res}, as well
as two words for the return address. This has the
effect of marking those bytes \(\object\).
(We use \(V\llbracket\cdot\rrbracket\) to denote updates to \(V\).)
%

\newcommand{\freebox}{\tikz \filldraw[fill=blue] (0,0) rectangle (10px,10px);}
\newcommand{\pubbox}{\tikz \filldraw[fill=lightgray] (0,0) rectangle (10px,10px);}
\newcommand{\objbox}{\tikz \filldraw[fill=yellow] (0,0) rectangle (10px,10px);}
\newcommand{\sealbox}{\tikz \filldraw[fill=red] (0,0) rectangle (10px,10px);}

@@

  \caption{Execution of example up through the return from {\tt f}. In stack diagram, addresses increase to the right, stack grows to the left, and boxes represent 4-byte words.}

>>>>

For a newly active function, every element that is available for use but uninitialized
is seen as \(\unsealed\). From the perspective of the caller, the callee has no obligations
regarding its use of \(\unsealed\) elements.

@@

\newcommand{\freebox}[1][10px]{\tikz \filldraw[fill=blue] (0,0) rectangle (#1,#1);}
\newcommand{\pubbox}[1][10px]{\tikz \filldraw[fill=lightgray] (0,0) rectangle (#1,#1);}
\newcommand{\objbox}[1][10px]{\tikz \filldraw[fill=yellow] (0,0) rectangle (#1,#1);}
\newcommand{\sealbox}[1][10px]{\tikz \filldraw[fill=red] (0,0) rectangle (#1,#1);}

\newcommand{\textbox}[1][]{\tikz \filldraw[fill=lightgray] (0,0) rectangle (30px,30px) node[pos=.5]{#1};}

@@

      \}}
  \end{subfigure}
  \begin{subfigure}{\columnwidth}
    \begin{tabular}{r l | l}
      \labeledrow{0:}{addi sp,sp,-20}{\(\mathbf{alloc} ~ (-20,20)\)}
      \labeledrow{4:}{sd ra,12(sp)}{}
      \labeledrow{8:}{sw a0,8(sp)}{}
      \labeledrow{12:}{sw zero,4(sp)}{}
      \labeledrow{16:}{jal f,ra}{\(\mathbf{call} ~ \emplist \)}
      \labeledrow{20:}{sw a0,0(sp)}{}
      \labeledrow{24:}{lw a4,4(sp)}{}
      \labeledrow{28:}{li a5,42}{}
      \labeledrow{32:}{bne a4,a5,L1}{}
      \labeledrow{36:}{lw a0,8(sp)}{}
      \labeledrow{40:}{sw a0,out}{}
      \labeledrow{44:}{j L2:}{}
      \labeledrow{L1, 48:}{lw a0,0(sp)}{}
      \labeledrow{52:}{sw a0,out}{}
      \labeledrow{L2, 56:}{ld ra,12(sp)}{}
      \labeledrow{60:}{addi sp,sp,20}{\(\mathbf{dealloc} ~ (0,20)\)}
      \labeledrow{64:}{jalr ra}{\(\mathbf{return}\)}
    \end{tabular}
  \end{subfigure}
  \begin{subfigure}{\columnwidth}
    \center
    \vspace{\abovedisplayskip}
    \(\textnormal{\large \dots} \pubbox[30px] \!\! \stackrel{\textsc{\large sp}}{\textbox[\tt res]}
    \stackrel{\textsc{\large 4(sp)}}{\textbox[\tt sens]}
    \stackrel{\textsc{\large 8(sp)}}{\textbox[\tt sec]}
    \stackrel{\textsc{\large 12(sp)} \hfill}{\textbox[\(\mathtt{ra_1}\)]\textbox[\(\mathtt{ra_2}\)]}
    \textnormal{\large \dots}\)
  \end{subfigure}

  \caption{Example: C and assembly code for {\tt main}, and layout of its stack frame; addresses increase to the right and the stack grows to the left.}
  \label{fig:main}
\end{figure}

@@

  \caption{Example: assembly code alternatives for {\tt f} as an attacker.}
  \label{fig:f}
\end{figure}

@@

The initial view \(V_0\) maps all stack addresses below \(\SP\) to \(\unsealed\) and the remainder of
memory to \(\public\). The sole used argument register, {\tt a0}, is mapped to \(\object\);
other caller-save registers are mapped to \(\unsealed\) and callee-save registers to \(\sealed\).
Step 1 allocates a word each for {\tt secret}, {\tt sensitive}, and {\tt res}, as well
as two words for the return address. This has the
effect of marking those bytes \(\object\).
(We use \(V\llbracket\cdot\rrbracket\) to denote updates to \(V\).)

@@

  \caption{Execution of example up through the return from {\tt f}. In stack diagrams, addresses increase to the right, stack grows to the left, and boxes represent 4-byte words.}
